Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex
add reporting related paragraphs. #14

% Define custom color
\definecolor{CustomBlue}{rgb}{0.25, 0.41, 0.88} % RoyalBlue
% Set up hyperref with the custom citecolor
\hypersetup{
    pdftitle={\@title},
    pdfauthor={\@author},
    pdfsubject={\@subject},
    pdfkeywords={HPC, HPCOps, Urban building, City Energy Simulation},
    bookmarksnumbered,bookmarksopen,linktocpage,
    colorlinks=true,
    citecolor=CustomBlue,
    linkcolor=CustomBlue,
    urlcolor=blue
}
\usepackage{cleveref}

@@

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth,page=1]{img-kub-workflow.pdf}
    \caption{Current Urban Building Workflow from localization to city energy simulation report.}
    \label{fig:kub-workflow}
\end{figure}

@@

@@

\caption{Different representations of a building using our LOD definition}
\label{fig:buildings}

\end{figure}

In \cref{fig:buildings}, we illustrate the different levels of details. 
\Cref{fig:building-lod0} displays the LOD-0 of a building with its bounding box. 
\Cref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. 
\Cref{fig:building-lod2} and~\cref{fig:building-lod2-zoom} display the LOD-2 representation using BIM. 
In \Cref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see \cref{fig:city-strasbourg-lod0}, and LOD-1, see \cref{fig:city-strasbourg-lod1}, representations.

@@

\subsubsection{Vegetation Modeling}

Including vegetation (trees) in our geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas had a significant impacts on building environment  . We use the OpenStreetMap database to obtain the metadata associated with the vegetation. In addition to the position of the trees, we can also obtain other information, such as the tree's height and species. The current strategy is as follows:

\begin{itemize}
\item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD). These geometric entities are parameterized so that a transformation can be applied.
\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best as we can (by searching around).
\item Creating a tree geometric model using an affine transformation of the reference tree model.
\end{itemize}

\subsubsection{Integration of all urban geometric components}

This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation). Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh. The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling). \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-feelpp-devops.pdf}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing.
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-feelpp-hpcops.pdf}
    \caption{CI/CD HPCOps for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{.7\linewidth}
    \centering
    \includegraphics[width=\linewidth,page=1]{img-ub-devops-hpcops.pdf}
    \caption{KUB standard DevOps}
    \label{fig:kub-devops}
\end{wrapfigure}
This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications.
It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth,page=2]{img-ub-devops-hpcops.pdf}
    \caption{Ktirio Urban Building HPCOps workflow}
    \label{fig:kub-hpcops}
\end{figure}

\subsection{Benchmarking KUB}
\label{sec:benchmarking}

>>>>

% Define custom color
\definecolor{CustomBlue}{rgb}{0.25, 0.41, 0.88} % RoyalBlue
% Set up hyperref with the custom citecolor
\hypersetup{
    pdftitle={\@title},
    pdfauthor={\@author},
    pdfsubject={\@subject},
    pdfkeywords={HPC, HPCOps, Urban building, City Energy Simulation},
    bookmarksnumbered,bookmarksopen,linktocpage,
    colorlinks=true,
    citecolor=CustomBlue,
    linkcolor=CustomBlue,
    urlcolor=blue
}

@@

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{img-kub-workflow.pdf}
    \caption{Current Urban Building Workflow from localization to city energy simulation report.}
    \label{fig:kub-workflow}
\end{figure}

@@

In addition to these exports, the simulator condenses, aggregates and saves relevant quantities on the fly to avoid having to manipulate large data volumes after the simulation. These metrics concern weather information, energy consumption and comfort assessment, and are exported in JSON format. The produced files are uploaded to a data management platform via the CI/CD pipeline, who is then in charge of notifying a different workflow in order to render insightful figures that showcase the simulation results.

Insights are presented in the form of a comprehensive report and are automatically deployed on a website built using the \textit{Antora} framework. End users are finally able to explore the simulation outputs in a detailed but malleable manner, for both the city and the building scales.

The figure \ref{fig:ktirio-cases-report} presents a gallery of city reports that are taken as test cases for the Urban Building pilot, as well as an example of a city report section showing the occlusion factor and heat flow plot.
\begin{figure}[htbp]
  \centering
  \subfloat[Gallery of test case cities reports\label{fig:city-gallery}]{%
    \includegraphics[width=0.45\textwidth]{img-compressed-city-gallery.png}
  }
  \hfill
  \subfloat[Section of a city report\label{fig:city-report-section}]{%
    \includegraphics[width=0.45\textwidth]{img-compressed-city-report-section.png}
  }
  \caption{Screenshots of the \url{https://cases.ktirio.fr} reporting website.}
  \label{fig:ktirio-cases-report}
\end{figure}

@@

\caption{Different representations of a building using our LOD definition}
\label{fig:buildings}
\end{figure}

In the figure~\ref{fig:buildings}, we illustrate the different levels of details. Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box. Panel~\ref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM. In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.

@@

\subsubsection{Vegetation Modeling}
Including vegetation (trees) in our geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas had a significant impacts on building environment  . We use the OpenStreetMap database to obtain the metadata associated with the vegetation. In addition to the position of the trees, we can also obtain other information, such as the tree's height and species. The current strategy is as follows:
\begin{itemize}
\item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD). These geometric entities are parameterized so that a transformation can be applied.
\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best as we can (by searching around).
\item Creating a tree geometric model using an affine transformation of the reference tree model.
\end{itemize}

\subsubsection{Integration of all urban geometric components}
This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation). Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh. The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling). \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-compressed-feelpp-devops.png}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing. 
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++. 
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-compressed-feelpp-hpcops.png}
    \caption{CI/CD HPCOps for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{.7\linewidth}
    \centering
    \includegraphics[width=\linewidth]{img-ub-devops.pdf}
    \caption{KUB standard DevOps}
    \label{fig:kub-devops}
\end{wrapfigure}
This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications. 
It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-ub-hpcops.pdf}
    \caption{Ktirio Urban Building HPCOps workflow}
    \label{fig:kub-hpcops}
\end{figure}

\subsection{Benchmarking KUB}
